A Survey of Range-Only SLAM Techniques and Sensors

### 2018-11-07 Paper.tex
Started editing sensor section
Up to the beginning of Wi-Fi

	\section{range only sensors}
	\label{range only sensors}
		There are a variety of sensors which can be utilized as range-only beacons for RO-SLAM. These range sensors refer to any device which involves a signal transmission that can be used for the range estimation without requiring line of sight. The most popular sensors can largely be broken down into two categories: acoustic based and radio frequency based. These two types of sensors both largely rely on the same principles for measuring distances, which are either signal time of flight, or signal attenuation through propagation through each respective medium. These beacons serve as the landmarks within the RO-SLAM algorithms and impact how the algorithms are implemented.

		%I think this section could use some more details.
		\subsection{Acoustic}

			Acoustic ranging systems are largely used with autonomous underwater vehicles (AUV) that operate in underwater locations. The reason for this is that radio waves experience strong attenuations in salt water environments. As Partan states, the issue of attenuation makes radio waves extremely impractical, thus making acoustics the logical alternative \cite{Partan2007}. Acoustics still suffer from a range of problems such as multipathing and propagation delays, but compared to the alternatives they perform adequately in underwater environments. Papers such as those by \cite{Erol-Kantarci2011} and \cite{Akyildiz2005} explore a wide variety of issues and possible solutions that relate to acoustic sensors, such as the added complexity of assuming a two dimensional versus a three dimensional environment, or the design challenges that accompany underwater deployment with regards to spatial correlation and power consumption.

		  	%Ehhhhh.. This section... I dunno if this section is necissary
			A unique implementation of an underwater acoustic beacon is the Dive'N'Rise (DNR) beacon presented by \cite{Erol2007}. These DNR beacons rise to the surface, receive their location through GPS, then sink into the water and transmit their coordinates. The distance between an agent and the transmitting beacon can be determined via time of flight from the transmissions and used in conjunction with the GPS location to determine a refined location for the beacon. A localization implementation using these beacons was accomplished by \cite{Erol2008}.

@@

			Radio frequency encompasses an extensive spectrum of devices capable of transmitting or receiving signals using radio frequencies (RF). There are two methods commonly utilized to determine distance from radio frequency. One is by examining the received signal strength indicator (RSSI) and the other is by measuring the time of flight of the signal. A system presented by \cite{Padmanabhan2000} processes RF signal strength and utilizes nearest neighbors heuristics to achieve localization based on said signal strength.  \cite{Kurth2003a} describes a method for using very small RF tags as beacons throughout the environment.  As a mobile robot moves throughout the environment it emits a query to which any RF tags that are within the transmission range respond. The robot then estimates the distance to the tag based on the delay. The response from the RF tags include a data tag which contains a unique ID number.

			Wireless Fidelity (wi-fi)  is the most popular beacon choice as existing networks are already prevalent in many indoor locations and they are generally low cost \cite{Youssef2005} \cite{Sen2013} \cite{Kotaru2015} \cite{Rea2017}. \cite{Youssef2005} presents a Horus system with the aim of high accuracy and low computation cost for wireless local area network location determining. \cite{Sen2013} proposes a method named CUPID which extracts information from the physical layer to process information allowing it to avoid the impact of multipathing. \cite{Kotaru2015} presents a design and implementation for its SpotFi system which can be deployed on top of existing wi-fi infrastructure. \cite{Rea2017} designed a new method for filtering range measurment specifically designed with the large noise found in indoor WiFi radios in mind.

@@

	A common focus of many recent papers has been the utilization of beacons for more than just robot to beacon range measurements. Many implementations now have beacons measure ranges to other beacons in addition to the robot. These beacon to beacon range measurements are then incorporated into existing EKF algorithms.

@@

	\section{Conclusion}
	\label{conclusion}
	This paper has introduced the motivation and practicality of range-only SLAM approaches. The variety of sensors used as range only beacons has been surveyed, along with initialization methods for their incorporation into the common SLAM algorithms. The variety of SLAM algorithms as they apply to range-only sensor data are surveyed here as well with a focus on the techniques that differentiate them and highlighting their strengths and weaknesses.

>>>>

	\section{range only sensors}
	\label{range only sensors}
		There are a variety of sensors which can be utilized as range-only beacons for RO-SLAM. These range sensors refer to any device which involves a signal transmission that can be used for the range estimation without requiring line of sight. The most popular sensors can largely be broken down into two categories: acoustic based and radio frequency based. These two types of sensors both largely rely on the same principles for measuring distances, which are either signal time of flight, or signal attenuation through propagation through each respective medium. These beacons serve as the landmarks within the RO-SLAM algorithms map and can have a significant impact how the algorithms are implemented.

		%I think this section could use some more details.

		%HOLY moly does acostic sensors need mor details
		\subsection{Acoustic}

			Acoustic ranging systems are largely used with autonomous underwater vehicles (AUV) that operate in underwater locations. The reason for this is that radio waves experience strong attenuations in salt water environments. As Partan states, the issue of attenuation makes radio waves extremely impractical, thus making acoustics the logical alternative \cite{Partan2007}. Acoustics still suffer from a range of problems such as multipathing and propagation delays, but compared to the alternatives they perform adequately in underwater environments. For those seeking additional information about the constraints imposed by underwater environments on acoustic sensors see \cite{Erol-Kantarci2011} and \cite{Akyildiz2005}. These papers explore a wide variety of issues and possible solutions that relate to acoustic sensors, such as the added complexity of assuming a two dimensional versus a three dimensional environment, or the design challenges that accompany underwater deployment with regards to spatial correlation and power consumption.

		  	%Ehhhhh.. This section... I dunno if this section is necissary
			A unique implementation of an underwater acoustic beacons is the Dive'N'Rise (DNR) beacon presented by \cite{Erol2007}. These DNR beacons rise to the surface, receive their location through GPS, then sink into the water and transmit their coordinates. The distance between an robot and the transmitting beacon can be determined via time of flight from the transmissions and used in conjunction with the GPS location to determine a refined location for the beacon. A localization implementation using these beacons was accomplished by \cite{Erol2008}.

@@

			This subsection encompasses an extensive spectrum of devices capable of transmitting or receiving signals using radio frequencies (RF). There are two methods commonly utilized to determine distance from radio frequency. One is by examining the received signal strength indicator (RSSI) and the other is by measuring the time of flight of the signal. A system presented by \cite{Padmanabhan2000} processes RF signal strength and utilizes nearest neighbors heuristics to achieve localization based on said signal strength.  \cite{Kurth2003a} describes a method for using very small RF tags as beacons in an environment.  As a mobile robot moves throughout the environment it emits a query to which any RF tags that are within the transmission range respond. The robot then estimates the distance to the tag based on the delay. The response from the RF tags include a data tag which contains a unique ID number.

			Wireless Fidelity (wi-fi)  is the a popular beacon choice as existing networks are already prevalent in many indoor locations and they are generally low cost \cite{Youssef2005} \cite{Sen2013} \cite{Kotaru2015} \cite{Rea2017}. \cite{Youssef2005} presents a system known as Horus with the aim of high accuracy and low computation cost for wireless local area network location determination. \cite{Sen2013} proposes a method named CUPID which extracts information from the physical layer to process information allowing it to avoid the impact of multipathing. \cite{Kotaru2015} presents a design and implementation for its SpotFi system which can be deployed on top of existing wi-fi infrastructure. \cite{Rea2017} designed a new method for filtering range measurment specifically designed with the large noise found in indoor WiFi radios in mind.

@@

	A common focus of many recent papers has been the utilization of beacons for more than just robot to beacon range measurements. Such implementations now use beacons to perform tasks such as measuring ranges to other beacons in addition to the robot. These beacon to beacon range measurements are then incorporated into existing EKF algorithms. Beacons are also utilized to off-load certain processing.

@@

	\section{Conclusion}
	\label{conclusion}
	This paper has introduced the motivation and practicality of RO-SLAM approaches. The variety of sensors used as range only beacons has been surveyed, along with initialization methods for their incorporation into the common SLAM algorithms. The variety of SLAM algorithms as they apply to range-only sensor data are surveyed here as well with a focus on the techniques that differentiate them and highlighting their strengths and weaknesses.
